%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0,0}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Yash Jawale} \\[14pt]
\normalsize
\href{https://yashjawale.github.io/}{\raisebox{-0.05\height}\faGlobe \ yashjawale.github.io} \ $|$ \ 
\href{https://github.com/yashjawale}{\raisebox{-0.05\height}\faGithub\ yashjawale} \ $|$ \ 
\href{https://linkedin.com/in/yashjawale}{\raisebox{-0.05\height}\faLinkedin\ yashjawale} \ $|$ \ 
\href{mailto:yash25.j@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ yash25.j@gmail.com} \ $|$ \ 
\href{tel:+919307918036}{\raisebox{-0.05\height}\faMobile \ +91 9307-9180-36} \\[8pt]
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
% \section{Summary}
% This CV is automatically generated and deployed using the \href{https://github.com/jitinnair1/autoCV}{autoCV} template along with GitHub Actions such that a new version of the CV is compiled, published and ready for use when the cv.tex file is updated. For details, \href{https://github.com/jitinnair1/autoCV}{click here}.

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Anything related to Computers excites me. I am a Computer Engineering student with a passion for Web Development. I've been developing websites for local businesses \textbf{\textit{since 2019}}, while simultaneously learning about new technologies.\\ I believe in creating simple \& thoughtful solutions that solve people's problems.

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	

\textbf{Dr. D. Y. Patil Institute of Technology, Pimpri, Pune 411018} & \hfill 
Sep 2021 - June 2025 \\ \vspace*{2mm}
B.E. Computer Engineering \\ 

\textbf{Modern College of Arts, Science \& Commerce, Shivajinagar, Pune 411005} & \hfill 
Aug 2019 - June 2021 \\ \vspace*{2mm}
H.S.C. 93.83\% \\ 

\textbf{St. Francis De Sales High School, Nagar Road, Pune 411014} & \hfill 
May 2019 \\ 
S.S.C. 85.40\% \\

\end{tabularx}
  
%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }

\multicolumn{2}{@{}X@{}}{
    \begin{joblong}{\href{https://github.com/yashjawale/peernews/}{PeerNews \faExternalLink*} \normalfont{\textit{[PHP, MySQL, TailwindCSS]}}}{June 2024}
        \item A public news app made with PHP. Allows all users to publish their own articles.
        \item Supports cover images for articles.
        \end{joblong}
}  \\
\\[-6pt]

\multicolumn{2}{@{}X@{}}{
    \begin{joblong}{\href{https://github.com/yashjawale/slidesync/}{SlideSync \faExternalLink*} \normalfont{\textit{[React, TailwindCSS, NodeJS, WebSockets]}}}{May 2023}
        \item Allows users to control their presentation with mobile device without requiring Bluetooth. Having internet connection as the only requirement.
        \item Created desktop client using ElectronJS, Mobile client with React \& PWA technology and a bridge server using NodeJS \& WebSockets.
        \item In process to be a full fledged open source project \& to be released to public.
        \end{joblong}
}  \\
\\[-6pt]

\multicolumn{2}{@{}X@{}}{
    \begin{joblong}{\href{https://github.com/shreedhar03/noteattendance/}{NoteAttendance \faExternalLink*} \normalfont{\textit{[React, PWA, NodeJS, Google Apps Script]}}}{Aug 2023}
        \item A Progressive Web App (PWA) which helps teachers take attendance of class \& updates the Google Sheet accordingly.
        \item Used Google App Scripts to create scheduled triggers to automatically export monthly reports to PDF.
        \item Developed as an InHouse project for the college.
        \end{joblong}
}  \\ 
\\[-6pt]

\multicolumn{2}{@{}X@{}}{
    \begin{joblong}{\href{https://acesdit.github.io/snippets/}{ACES Snippets \faExternalLink*} \normalfont{\textit{[AstroJS, TailwindCSS, GitHub Actions, Bash]}}}{Oct 2023}
        \item Collection of DataStructures/Algorithms and other useful snippets paired with a showcase website created as part of Club\'s Open Source month celebration.
        \item Created showcase website with Astro \& utilized GitHub Actions to translate user contributed code files to MD files for displaying on website.
        \end{joblong}
}  \\ 
\\[-6pt]

\multicolumn{2}{@{}X@{}}{
    \begin{joblong}{\href{https://aces.dypvp.edu.in/}{ACES Website \faExternalLink*} \normalfont{\textit{[NextJS, TailwindCSS, Sanity]}}}{Nov 2023}
        \item Created new website for ACES DIT with NextJS.
        \item Utilizes Sanity CMS for storing data \& dynamically displays it on appropriate pages.
        \end{joblong}
}  \\ 
\\[-6pt]

\end{tabularx}

%----------------------------------------------------------------------------------------
%	POSITIONS
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }

    \multicolumn{2}{@{}X@{}}{
        \begin{joblong}{XDE Studios Pvt. Ltd. - \normalfont{\textit{Web Dev Intern}}}{Jan 2024 - Present}
            \item Designed \& developed solutions for clients \& internal projects.
            \item Assisted in deployment \& support of projects.
            \end{joblong}
    }  \\ 
    \\[-6pt]

    \multicolumn{2}{@{}X@{}}{
        \begin{joblong}{Software Development Cell, DIT Pimpri - \normalfont{\textit{Frontend Web Dev Intern}}}{Dec 2023 - Present (Part Time)}
            \item Responsible for design \& development of new ERP application for college.
            \item Collaborated with rest of the team to develop new features \& find solutions to problems of existing system.
            \end{joblong}
    }  \\ 
    \\[-6pt]

\end{tabularx}

%----------------------------------------------------------------------------------------
%	VOLUNTEERING
%----------------------------------------------------------------------------------------
\section{Volunteering}

\begin{tabularx}{\linewidth}{@{}l X@{}}	

\textbf{Sr. Technical Head, Association of Computer Engineering Students} & \hfill 
2023-24 \\ \vspace*{1mm}
Responsible for guiding Jr. Technical Heads \& aiding in technical tasks. \\ 

\textbf{Web Dev Member Lead, Google Developer Student Clubs DIT} & \hfill 
2023-24 \\ \vspace*{1mm}
Responsible for helping GDSC in Web Development Domain. \\ 

\textbf{Jr. Technical Head, Association of Computer Engineering Students} & \hfill 
2022-23 \\ 
Designed posters for events, posted blogs on ACES WordPress, Prepped lab computers with Bash. \\ 

\end{tabularx}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Languages} &  \normalsize{HTML, CSS, JavaScript, PHP, TypeScript, C++, Python, Java, Bash}\\
\textbf{Databases} &  \normalsize{MySQL, SQLite, PostgreSQL, MongoDB, Firestore}\\
\textbf{Web Dev}  &  \normalsize{React, NextJS, AstroJS, Angular,  Flask, NodeJS, \textbf{\textit{WordPress}}, WiX, Framer}\\
\textbf{Administration} & \normalsize{Experience with multiple Linux Distributions, Google Workspace Admin}\\
\textbf{DevOps}  &  \normalsize{Git, GitHub, GitHub Actions,  Docker}\\
\end{tabularx}


%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications \& Achievements}
\begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{CS50x - Harvard University} & \normalsize{Gained understanding of various Computer Science Concepts \& completed the course by solving assignments \& final project.}\\
    \textbf{Cisco Networking Basics} &  \normalsize{Gained understanding about Computer Networks}\\
    \textbf{Hacktoberfest 8 to 10}  &  \normalsize{ Contributed to real world open source repositories, conducted session for SE-TE students on Git \& GitHub. Maintained repositories under ACES. }\\
    \textbf{Google Cloud 30 Days Challenge} &  \normalsize{Learned about various Cloud services \& Completed career practioner program}\\
\end{tabularx}

\vspace*{5mm}
\center{\footnotesize Last updated: \today}

\end{document}
